---
output: github_document
---

# rspell

<!-- badges: start -->
[![R-CMD-check](https://github.com/rfsaldanha/rspell/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rfsaldanha/rspell/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package aims to provide grammar check in R, specially for RStudio users editing notebooks. As some tools like Grammarly and LanguageTools are not (yet) directly integrated to the IDE, this is a temporary solution.

`rspell` uses the [LanguageTool API](https://languagetool.org/http-api/) and can verify grammar for several languages and was inspired by the [`ggspell`](https://github.com/nicucalcea/ggspell)package.

## Usage

First, install the package.

```{r eval=FALSE}
remotes::install_github("rfsaldanha/rspell")
```

Then, select some text on RStudio (notebook, script, documentation...) and run the `check_selection` command at the console.

```{r eval=FALSE}
rspell::check_selection()
```

Possible grammar errors will be shown at the console, and you will be asked to modify or not the text.

## Language selection

The package will observe if a language was set on project configuration. Set this option, even for English.

Tools --> Project Options... --> Spelling --> Main dictionary language

If this is not defined (`Default` option), the package will let the LanguageTool API try to determine the language based on the text.

You can also manually specify the language ([available options](https://api.languagetoolplus.com/v2/languages) at the API).

```{r eval=FALSE}
rspell::check_selection(language = "FR")
```

## Add-in and keyboard shortcut

For a faster use, you can use the package's RStudio add-in. After installing the package, it will be available at the add-in list. You can also map a [keyboard shortcut](https://support.posit.co/hc/en-us/articles/206382178-Customizing-Keyboard-Shortcuts-in-the-RStudio-IDE) for it, like `Ctrl+g`.

## Modify or just list the errors

It is possible to just show the errors without asking to modificate the selection.

```{r eval=FALSE}
rspell::check_selection(ask_modify = FALSE)
```



